Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
change the content of Overview

The variables included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data. In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.

>>>>

The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data. In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.
